### 2022-05-27 chapters/04-chapter-4.tex
txs auto checkin

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[]
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\multicolumn{1}{|c|}{ID} &
		\multicolumn{1}{c|}{Service (Fungsi)} &
		\multicolumn{1}{l|}{Extra Latency} &
		\multicolumn{1}{l|}{User} &
		Keterangan \\ \hline
		I1 &
		CheckoutService (placeorder) &
		100ms &
		25 &
		Kasus extra latency \#1 \\ \hline
		I2 &
		CheckoutService (placeorder) &
		250ms &
		25 &
		Kasus extra latency \#2 \\ \hline
		I3 &
		CheckoutService (placeorder) &
		350ms &
		25 &
		Kasus extra latency \#3 \\ \hline
		I4 &
		CheckoutService (placeorder) &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular} \\ \hline
		I5 &
		CheckoutService (placeorder) &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular} \\ \hline
		I6 &
		CheckoutService (placeorder) &
		- &
		25 &
		Kasus peningkatan kerja CPU \\ \hline
		\multirow{4}{*}{I7} &
		CheckoutService (placeorder) &
		\multirow{4}{*}{250ms} &
		\multirow{4}{*}{25} &
		\multirow{4}{*}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency\\  dengan beberapa service\end{tabular}} \\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}ProductCatalog (getproduct\\ listproducts)\end{tabular} &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService (getquote) &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService \\ (listrecommendations)\end{tabular} &
		&
		&
		\\ \hline
	\end{tabular}
\end{table}

>>>>

%		\begin{longtable}[l]{  @{}| p{0.7cm} | p{5cm} | p{2cm} | p{2cm} | p{4cm} | @{} }
%			\caption{Kasus-kasus pengujian}
%			\label{testcase-i}                                                           
%			\\ \hline
%			\centering\bfseries{ID} & \centering\bfseries{Service (Fungsi)} & \centering\bfseries{Extra Latency} & \centering\bfseries{User} & \centering\bfseries{Keterangan} \tabularnewline \hline
%			\endfirsthead
%			I1 & CheckoutService (placeorder) &  \centering{100ms} & \centering{25} & Kasus extra latency \#1 \\ \hline
%				
%		\end{longtable}

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
% \usepackage{multirow}
% \usepackage[table,xcdraw]{xcolor}
% If you use beamer only pass "xcolor=table" option, i.e. \documentclass[xcolor=table]{beamer}
\begin{table}[]
	\begin{tabular}{@{}llccl@{}}
		\toprule
		\rowcolor[HTML]{009901} 
		\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{ID}}} &
		\multicolumn{1}{c}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Service (Fungsi)}}} &
		\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{Extra Latency}}} &
		\multicolumn{1}{l}{\cellcolor[HTML]{009901}{\color[HTML]{FFFFFF} \textbf{User}}} &
		{\color[HTML]{FFFFFF} \textbf{Keterangan}} \\ \midrule
		\multicolumn{1}{|l|}{I1} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{100ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#1} \\ \midrule
		\multicolumn{1}{|l|}{I2} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#2} \\ \midrule
		\multicolumn{1}{|l|}{I3} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{350ms} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus extra latency \#3} \\ \midrule
		\multicolumn{1}{|l|}{I4} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{75} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \midrule
		\multicolumn{1}{|l|}{I5} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{250ms} &
		\multicolumn{1}{c|}{150} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency \\ dengan peningkatan user \#1\end{tabular}} \\ \midrule
		\multicolumn{1}{|l|}{I6} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{-} &
		\multicolumn{1}{c|}{25} &
		\multicolumn{1}{l|}{Kasus peningkatan kerja CPU} \\ \midrule
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{CheckoutService (placeorder)} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}ProductCatalog (getproduct\\ listproducts)\end{tabular}} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{} &
		\multicolumn{1}{l|}{ShippingService (getquote)} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{c|}{} &
		\multicolumn{1}{l|}{} \\ \cmidrule(lr){2-2}
		\multicolumn{1}{|l|}{\multirow{-4}{*}{I7}} &
		\multicolumn{1}{l|}{\begin{tabular}[c]{@{}l@{}}RecommendationService \\ (listrecommendations)\end{tabular}} &
		\multicolumn{1}{c|}{\multirow{-4}{*}{250ms}} &
		\multicolumn{1}{c|}{\multirow{-4}{*}{25}} &
		\multicolumn{1}{l|}{\multirow{-4}{*}{\begin{tabular}[c]{@{}l@{}}Kasus extra latency\\  dengan beberapa service\end{tabular}}} \\ \bottomrule
	\end{tabular}
\end{table}
